---
title: "gp contest data analysis"
author: "CDL"
date: "10/3/2018"
output: html_document
---

Analysis # 1
---

Objective: To get school ranks at District/Block/Cluster/GP levels
Method:
- Encode Yes/No to 1/0
- Aggregate all subject wise numbers at a school level
- Adding these scores to get a combined score
- Divide the combined score by the number of students to get mean score per student
- Ranking schools at overall/district/block/cluster/gp levels using the variable `mean score per student`

```{r Datasets to read}
datasets_to_read <- Sys.glob("../data/*/*.csv")
datasets_to_read <- datasets_to_read[!datasets_to_read %in% "../data/gp_contest_csv_files_2017-18/gp_contest_class_6_2017-18.csv"]

```



```{r Reading datasets}
read_dataset <- function(class_data_to_read){
class_dataset <- read.csv(class_data_to_read, stringsAsFactors = FALSE, check.names = FALSE)

if(grepl(class_data_to_read,pattern = "gp_contest_class_4_2017")){
 index_to_rename <- which(names(class_dataset) == 'SNAME')
 names(class_dataset)[index_to_rename] <- 'SCODE'
 names(class_dataset)[index_to_rename+1] <- 'SNAME'
}
return(class_dataset)
}

```


```{r getting school-class wise perfromance}
library(dplyr)
static_cols <- c("DIST", "BLK", "CLUST", "GPCODE", "GPNAME", "SCODE", "SNAME", "STORY_ID", "ENTERED_AT", "DATE_OF_VISIT", "RESPONDENT_TYPE", "Gender", "Class visited")

get_school_class_per <- function(class_data_to_read){
# class_data_to_read <- datasets_to_read[[4]]

class_dataset <- read_dataset(class_data_to_read)  
  
subject_cols <- dplyr::setdiff(names(class_dataset), static_cols)  

# Trimming all subject cols & Encoding all subject cols from Yes/No to 1/0
for(sub in 1:length(subject_cols)){
  class_dataset[,subject_cols[[sub]]] <- stringr::str_trim(class_dataset[,subject_cols[[sub]]])
  class_dataset[,subject_cols[[sub]]] <- ifelse(class_dataset[, subject_cols[[sub]]] == "Yes",1,0)
}

class_dataset$year <- paste0(unique(sort(lubridate::year(as.Date(class_dataset$DATE_OF_VISIT)))),collapse = "-")
class_dataset <- class_dataset[,c("DIST", "BLK", "CLUST", "GPCODE", "GPNAME", "SCODE", "SNAME","Class visited","year", subject_cols)]
# browser()
school_subject_sum <- class_dataset %>% group_by(DIST, BLK, CLUST, GPCODE, GPNAME, SCODE, SNAME,`Class visited`,year) %>% summarise_all(c('sum'))
school_count <- class_dataset %>% group_by(DIST, BLK, CLUST, GPCODE, GPNAME, SCODE, SNAME,`Class visited`,year) %>% summarise(total_student = length(DIST))

school_df <- dplyr::left_join(school_subject_sum, school_count, by=NULL)
school_df$total_marks <- rowSums(school_df[,subject_cols])
school_df$mean_marks <- school_df$total_marks/school_df$total_student
school_df$rank_overall <- rank(-school_df$mean_marks,na.last = "keep",ties.method = "first")
  
district_rank <- school_df %>%
    group_by(DIST) %>%
    mutate(dist_rank = order(order(mean_marks, decreasing=TRUE)))

block_rank <- district_rank %>%
    group_by(DIST,BLK) %>%
    mutate(block_rank = order(order(mean_marks, decreasing=TRUE)))

cluster_rank <- block_rank %>%
    group_by(DIST,BLK,CLUST) %>%
    mutate(cluster_rank = order(order(mean_marks, decreasing=TRUE)))

gp_rank <- cluster_rank %>%
    group_by(DIST,BLK,CLUST,GPCODE,GPNAME) %>%
    mutate(gp_rank = order(order(mean_marks, decreasing=TRUE)))

rm(district_rank,block_rank, cluster_rank)
gp_rank <- gp_rank[,!names(gp_rank) %in% subject_cols]
print(glue::glue("{class_data_to_read} finished processing .. "))
return(gp_rank)

}


all_results <- lapply(datasets_to_read, get_school_class_per)

all_rank_df <- dplyr::bind_rows(all_results)
data.table::fwrite(all_rank_df,"../data/school_rank.csv",row.names = FALSE)

```

```{r Total students (gender wise) for a selected school-class}
get_total_students <- function(class_data_to_read){
  class_dataset <- read_dataset(class_data_to_read)  
  class_dataset$year <- paste0(unique(sort(lubridate::year(as.Date(class_dataset$DATE_OF_VISIT)))),collapse = "-")
  class_dataset <- class_dataset[,c("DIST", "BLK", "CLUST", "GPCODE", "GPNAME", "SCODE", "SNAME","Class visited","year","Gender")]
  class_gender_profile <- class_dataset %>% group_by(DIST, BLK, CLUST, GPCODE, GPNAME, SCODE, SNAME,`Class visited`,year,Gender) %>% summarise(total_students = length(DIST))
  print(glue::glue("{class_data_to_read} finished processing .. "))
  return(class_gender_profile)
}

class_profile <- lapply(datasets_to_read, get_total_students)

class_profile_df <- dplyr::bind_rows(class_profile)
data.table::fwrite(class_profile_df,"../data/class_gender_profile.csv",row.names = FALSE)

```

